Fractional Types

### 2019-11-20 fracGC/p.tex
more cleanup code

\paragraph*{Temporary Storage using Ancilla Bits.} The universality of
the Toffoli gate for classical reversible computing and of the
universality of the Toffol-Hadamard gates for quantum computing should
not distract from efficiency and safety concerns. The theorems proving
universality (i) assume that temporary storage (often called
\emph{ancilla bits}) may be used~\cite{Toffoli:1980}, and (ii) that
this temporary storage is returned to its initial state before
de-allocation. Indeed if no temporary storage is allowed, the Toffoli
gate is not
universal~\cite{DBLP:conf/innovations/AaronsonGS17,DBLP:journals/corr/Xu15e}
and as would be expected the more temporary storage is allowed, the
more efficient certain computations could become.

@@

The first example below illustrates the basic functionality of
ancillae. The circuit has one input and one output. Immediately after
receiving the input, the circuit generates an ancilla wire and its
corresponding gc process (first line in the Agda definition). The
original input and the ancilla wire interact using two
\AgdaFunction{CNOT} gates, after which the ancilla wire is redirected
to the output (second line in the Agda code). Finally the original
input is gc'ed (third line in the Agda code). The entire circuit is
extensionally equivalent to the identity function.

\begin{center}
\input{idpic.tikz}
\end{center}

\EtaEpsilonExamples{}

@@

>>>>

\paragraph*{Temporary Storage using Ancilla Bits.} The universality of
the Toffoli gate for classical reversible computing and of the
universality of the Toffoli-Hadamard gates for quantum computing should
not distract from efficiency and safety concerns. The theorems proving
universality (i) assume that temporary storage (often called
\emph{ancilla bits}) may be used~\cite{Toffoli:1980}, and (ii) that
this temporary storage is returned to its initial state before
de-allocation. Indeed if no temporary storage is allowed, the Toffoli
gate is not
universal~\cite{DBLP:conf/innovations/AaronsonGS17,DBLP:journals/corr/Xu15e}
and as would be expected the more temporary storage is allowed, the
more efficient certain computations could become.

@@

The first example below illustrates the basic functionality of
ancillae. The Agda code is written in a style that reveals the
intermediate steps for convenience. The circuit has one input and one
output. Immediately after receiving the input, the circuit generates
an ancilla wire and its corresponding gc process (first two steps in
the Agda definition). The original input and the ancilla wire interact
using two \AgdaFunction{CNOT} gates, after which the ancilla wire is
redirected to the output (next three steps in the Agda code). Finally
the original input is gc'ed (last two steps in the Agda code). The
entire circuit is extensionally equivalent to the identity function.

\medskip
\begin{center}
\input{idpic.tikz}
\end{center}

\EtaEpsilonExampleone{}

@@

\EtaEpsilonExampletwo{}
